Investigating soundscapes perception through acoustic scenes simulation

### 2018-01-31 lafaySimulatedScenePerception.tex
fig size

\begin{figure}[t]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/xp4_note_13}\label{fig:xp2_Asubject}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/xp4_note_15}\label{fig:xp2_Ascene}}
        \caption{Distribution of the mean perceived pleasantness per subject $\mathcal{A}_{subject}$ (a) and the mean perceived pleasantness per scene $\mathcal{A}_{scene}$ (b) versus scene type. Black stars in subfigure (a) stand for the detected outlier, \ie~subject 7.}\label{fig:xp2A}
\end{figure}

>>>>

\begin{figure}[t]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=.48\linewidth]{gfx/xp4_note_13}\label{fig:xp2_Asubject}}
        \subfloat[]
        {\includegraphics[width=.48\linewidth]{gfx/xp4_note_15}\label{fig:xp2_Ascene}}
        \caption{Distribution of the mean perceived pleasantness per subject $\mathcal{A}_{subject}$ (a) and the mean perceived pleasantness per scene $\mathcal{A}_{scene}$ (b) versus scene type. Black stars in subfigure (a) stand for the detected outlier, \ie~subject 7.}\label{fig:xp2A}
\end{figure}
